Using a Two-Layer Neural Network and Physicochemical Properties to Classify Glass for Forensic Analysis

### 2017-06-26 Paper/paper.tex
Paper Edits
Paper edits

\subsection{Network Architecture}
\label{sec4.1}
The standard neural network architecture for pattern recognition problems is the multi-layer perceptron with tangent-sigmoid transfer functions in the hidden layers and \emph{softmax} transfer functions in the output layer. For most problems, including a fairly simple one like ours, one hidden layer usually suffices. Thus, we will implement a two-layer perceptron. If the results of the network are unsatisfactory after training and testing with one hidden layer, we will retrain with an additional hidden layer, but we do not anticipate having to do this. The \emph{tansig} transfer function is usually preferred to the \emph{logsig} transfer function in the hidden layers since it produces outputs (which are inputs to the next layer) that are centered near zero, whereas the \emph{logsig} transfer function always produces positive outputs.

@@

Now that we have chosen a network architecture, we can calculate the network output. The output from the hidden layer (the input to the output layer) can be calculated as 
\[
\mathbf{a^{1}} = \textbf{logsig}(\mathbf{W^{1}}\mathbf{p} + \mathbf{b^{1}}), 
\] 
while the output from the output layer is 
\[ 
\mathbf{a^{2}} = \textbf{softmax}(\mathbf{W^{2}}\mathbf{a^{1}} + \mathbf{b^{2}}). 
\]
The network architecture can be seen in \textbf{Figure 1} below. 
\begin{figure}[H]
\includegraphics[width = 6in]{figs/network.png}
\caption{Two-Layer Perceptron Used to Classify Glass Samples}
\end{figure}

>>>>

\subsection{Network Architecture}
\label{sec4.1}
The standard neural network architecture for pattern recognition problems is the multi-layer perceptron with tangent-sigmoid transfer functions in the hidden layers and \emph{softmax} transfer functions in the output layer. For most problems, including a fairly simple one like ours, one hidden layer usually suffices. Thus, we will implement a two-layer perceptron. If the results of the network are unsatisfactory after training and testing with one hidden layer, we will retrain with an additional hidden layer, but we do not anticipate having to do this. The \emph{tansig} transfer function is usually preferred to the \emph{tansig} transfer function in the hidden layers since it produces outputs (which are inputs to the next layer) that are centered near zero, whereas the \emph{tansig} transfer function always produces positive outputs.

@@

Now that we have chosen a network architecture, we can calculate the network output. The output from the hidden layer (the input to the output layer) can be calculated as 
\[
\mathbf{a^{1}} = \textbf{tansig}(\mathbf{W^{1}}\mathbf{p} + \mathbf{b^{1}}), 
\] 
while the output from the output layer is 
\[ 
\mathbf{a^{2}} = \textbf{softmax}(\mathbf{W^{2}}\mathbf{a^{1}} + \mathbf{b^{2}}). 
\]
The network architecture can be seen in \textbf{Figure 1} below. 
\begin{figure}[H]
\includegraphics[width = 6in]{figs/network.png}
\caption{Two-Layer Perceptron Used to Classify Glass Samples}
\end{figure}
